### 2021-02-16 paper/natastron/Publication/Send/bblpaper.tex
prepped upload

	\bibitem{barnes2007}
	\bibinfo{author}{Barnes, S.~A.}
	\newblock \bibinfo{title}{Ages for {{Illustrative Field Stars Using
				Gyrochronology}}: {{Viability}}, {{Limitations}}, and {{Errors}}}.
	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
	\textbf{\bibinfo{volume}{669}}, \bibinfo{pages}{1167} (\bibinfo{year}{2007}).

	\bibitem{meibom+2015}
	\bibinfo{author}{Meibom, S.} \emph{et~al.}
	\newblock \bibinfo{title}{A spin-down clock for cool stars from observations of
		a 2.5-billion-year-old cluster}.
	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
	\bibinfo{pages}{589} (\bibinfo{year}{2015}).

	\bibitem{leiner+2019}
	\bibinfo{author}{Leiner, E.}, \bibinfo{author}{Mathieu, R.~D.},
	\bibinfo{author}{Vanderburg, A.}, \bibinfo{author}{Gosnell, N.~M.} \&
	\bibinfo{author}{Smith, J.~C.}
	\newblock \bibinfo{title}{Blue {{Lurkers}}: {{Hidden Blue Stragglers}} on the
		{{M67 Main Sequence Identified}} from {{Their Kepler}}/{{K2 Rotation
				Periods}}}.
	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
	\textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).

@@

	\bibitem{silvaaguirre+2015}
	\bibinfo{author}{Silva~Aguirre, V.} \emph{et~al.}
	\newblock \bibinfo{title}{Ages and fundamental properties of {{Kepler}}
		exoplanet host stars from asteroseismology}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	\textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127} (\bibinfo{year}{2015}).

	\bibitem{angus+2015}
	\bibinfo{author}{Angus, R.}, \bibinfo{author}{Aigrain, S.},
	\bibinfo{author}{{Foreman-Mackey}, D.} \& \bibinfo{author}{McQuillan, A.}
	\newblock \bibinfo{title}{Calibrating gyrochronology using {{Kepler}}
		asteroseismic targets}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	\textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787} (\bibinfo{year}{2015}).

@@

	\bibitem{davies+2015}
	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
	\newblock \bibinfo{title}{Asteroseismic inference on rotation, gyrochronology
		and planetary system dynamics of 16 {{Cygni}}}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	\textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959} (\bibinfo{year}{2015}).

	\bibitem{vansaders+2016}
	\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
	\newblock \bibinfo{title}{Weakened magnetic braking as the origin of
		anomalously rapid rotation in old field stars}.
	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
	\bibinfo{pages}{181} (\bibinfo{year}{2016}).

@@

	\bibitem{davies+2016}
	\bibinfo{author}{Davies, G.~R.} \emph{et~al.}
	\newblock \bibinfo{title}{Oscillation frequencies for 35 {{Kepler}} solar-type
		planet-hosting stars using {{Bayesian}} techniques and machine learning}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	\textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183} (\bibinfo{year}{2016}).

@@

	\bibitem{benomar+2018}
	\bibinfo{author}{Benomar, O.} \emph{et~al.}
	\newblock \bibinfo{title}{Asteroseismic detection of latitudinal differential
		rotation in 13 {{Sun}}-like stars}.
	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{361}},
	\bibinfo{pages}{1231} (\bibinfo{year}{2018}).

@@

	\bibitem{lorenzo-oliveira+2019}
	\bibinfo{author}{{Lorenzo-Oliveira}, D.} \emph{et~al.}
	\newblock \bibinfo{title}{Constraining the evolution of stellar rotation using
		solar twins}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	\textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68} (\bibinfo{year}{2019}).

@@

	\bibitem{barnes2010}
	\bibinfo{author}{Barnes, S.~A.}
	\newblock \bibinfo{title}{A {{Simple Nonlinear Model}} for the {{Rotation}} of
		{{Main}}-sequence {{Cool Stars}}. {{I}}. {{Introduction}}, {{Implications}}
		for {{Gyrochronology}}, and {{Color}}-{{Period Diagrams}}}.
	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
	\textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222} (\bibinfo{year}{2010}).

>>>>

	\bibitem{barnes2007}
	\bibinfo{author}{{Barnes}, S.~A.}
	\newblock \bibinfo{title}{{Ages for Illustrative Field Stars Using
	  Gyrochronology: Viability, Limitations, and Errors}}.
	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
	  \textbf{\bibinfo{volume}{669}}, \bibinfo{pages}{1167--1189}
	  (\bibinfo{year}{2007}).
	\newblock \eprint{0704.3068}.

	\bibitem{meibom+2015}
	\bibinfo{author}{{Meibom}, S.} \emph{et~al.}
	\newblock \bibinfo{title}{{A spin-down clock for cool stars from observations
	  of a 2.5-billion-year-old cluster}}.
	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{517}},
	  \bibinfo{pages}{589--591} (\bibinfo{year}{2015}).
	\newblock \eprint{1501.05651}.

	\bibitem{leiner+2019}
	\bibinfo{author}{{Leiner}, E.}, \bibinfo{author}{{Mathieu}, R.~D.},
	  \bibinfo{author}{{Vanderburg}, A.}, \bibinfo{author}{{Gosnell}, N.~M.} \&
	  \bibinfo{author}{{Smith}, J.~C.}
	\newblock \bibinfo{title}{{Blue Lurkers: Hidden Blue Stragglers on the M67 Main
	  Sequence Identified from Their Kepler/K2 Rotation Periods}}.
	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
	  \textbf{\bibinfo{volume}{881}}, \bibinfo{pages}{47} (\bibinfo{year}{2019}).
	\newblock \eprint{1904.02169}.

@@

	\bibitem{silvaaguirre+2015}
	\bibinfo{author}{{Silva Aguirre}, V.} \emph{et~al.}
	\newblock \bibinfo{title}{{Ages and fundamental properties of Kepler exoplanet
	  host stars from asteroseismology}}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	  \textbf{\bibinfo{volume}{452}}, \bibinfo{pages}{2127--2148}
	  (\bibinfo{year}{2015}).
	\newblock \eprint{1504.07992}.

	\bibitem{angus+2015}
	\bibinfo{author}{{Angus}, R.}, \bibinfo{author}{{Aigrain}, S.},
	  \bibinfo{author}{{Foreman-Mackey}, D.} \& \bibinfo{author}{{McQuillan}, A.}
	\newblock \bibinfo{title}{{Calibrating gyrochronology using Kepler
	  asteroseismic targets}}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	  \textbf{\bibinfo{volume}{450}}, \bibinfo{pages}{1787--1798}
	  (\bibinfo{year}{2015}).
	\newblock \eprint{1502.06965}.

@@

	\bibitem{davies+2015}
	\bibinfo{author}{{Davies}, G.~R.} \emph{et~al.}
	\newblock \bibinfo{title}{{Asteroseismic inference on rotation, gyrochronology
	  and planetary system dynamics of 16 Cygni}}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	  \textbf{\bibinfo{volume}{446}}, \bibinfo{pages}{2959--2966}
	  (\bibinfo{year}{2015}).
	\newblock \eprint{1411.1359}.

	\bibitem{vansaders+2016}
	\bibinfo{author}{{van Saders}, J.~L.} \emph{et~al.}
	\newblock \bibinfo{title}{{Weakened magnetic braking as the origin of
	  anomalously rapid rotation in old field stars}}.
	\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{529}},
	  \bibinfo{pages}{181--184} (\bibinfo{year}{2016}).
	\newblock \eprint{1601.02631}.

@@

	\bibitem{davies+2016}
	\bibinfo{author}{{Davies}, G.~R.} \emph{et~al.}
	\newblock \bibinfo{title}{{Oscillation frequencies for 35 Kepler solar-type
	  planet-hosting stars using Bayesian techniques and machine learning}}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	  \textbf{\bibinfo{volume}{456}}, \bibinfo{pages}{2183--2195}
	  (\bibinfo{year}{2016}).
	\newblock \eprint{1511.02105}.

@@

	\bibitem{benomar+2018}
	\bibinfo{author}{{Benomar}, O.} \emph{et~al.}
	\newblock \bibinfo{title}{{Asteroseismic detection of latitudinal differential
	  rotation in 13 Sun-like stars}}.
	\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{361}},
	  \bibinfo{pages}{1231--1234} (\bibinfo{year}{2018}).
	\newblock \eprint{1809.07938}.

@@

	\bibitem{lorenzo-oliveira+2019}
	\bibinfo{author}{{Lorenzo-Oliveira}, D.} \emph{et~al.}
	\newblock \bibinfo{title}{{Constraining the evolution of stellar rotation using
	  solar twins}}.
	\newblock \emph{\bibinfo{journal}{Mon. Not. R. Astron. Soc.}}
	  \textbf{\bibinfo{volume}{485}}, \bibinfo{pages}{L68--L72}
	  (\bibinfo{year}{2019}).
	\newblock \eprint{1903.02630}.

@@

	\bibitem{barnes2010}
	\bibinfo{author}{{Barnes}, S.~A.}
	\newblock \bibinfo{title}{{A Simple Nonlinear Model for the Rotation of
	  Main-sequence Cool Stars. I. Introduction, Implications for Gyrochronology,
	  and Color-Period Diagrams}}.
	\newblock \emph{\bibinfo{journal}{Astrophys. J.}}
	  \textbf{\bibinfo{volume}{722}}, \bibinfo{pages}{222--234}
	  (\bibinfo{year}{2010}).
